Generating Simulated Data

### 2021-04-30 docs/SimData.Rmd
add catch and catch-length comps in Gavin's format

Now write input files in Gavin's format to have surveys together in one file:

@@

#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    tidyr::spread(sizebin, sumlen) %>%
    ungroup() %>%
    dplyr::mutate(inpN = rowSums(.[,-(1:2)], na.rm = TRUE)) %>%
    dplyr::mutate(type = 0) %>%
    dplyr::mutate(survey = s) %>%
    dplyr::mutate_at(vars(contains("sizebin")), ~./inpN) %>%
    dplyr::select(survey, year, species, type, inpN, everything())

@@

@@

Survey and catch datasets in Gavin's suggested format (all surveys together, all fleets together):

@@

#multiple surveys named in list object, use as filename
for(s in names(survObsBiom)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svbio <- survObsBiom[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, year, atoutput) %>%
    dplyr::rename(biomass = atoutput) %>%
    dplyr::mutate(survey = s,
                  CV = 0.2) %>% #placeholder, can get actual value used to generate from config files
    dplyr::select(survey, year, species, everything()) %>%
    dplyr::arrange(survey, species, year)

@@

>>>>

Now write input files in Gavin's format to have surveys together in one file. Note that this is just a test. The folder has two different survey and two different fishery configurations; they are not independent. Also, fishery catch is not currently separated into fleets. We wouldn't use all of these in an input file. Also add fishery length comps:

@@

#multiple surveys named in list object, add to file
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    tidyr::spread(sizebin, sumlen) %>%
    ungroup() %>%
    dplyr::mutate(inpN = rowSums(.[,-(1:2)], na.rm = TRUE)) %>%
    dplyr::mutate(type = 0) %>%
    dplyr::mutate(survey = s) %>%
    dplyr::mutate_at(vars(contains("sizebin")), ~./inpN) %>%
    dplyr::select(survey, year, species, type, inpN, everything())

@@

#requires function below
catchlen_ss <- read_savedfisheries(d.name, "catchLen")

allfishlenbin <- tibble()
for(f in names(catchlen_ss)){
  #arrange into long format: year, Species, agecl, length 
  fishlenbin <- catchlen_ss[[f]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    tidyr::spread(sizebin, sumlen) %>%
    ungroup() %>%
    dplyr::mutate(inpN = rowSums(.[,-(1:2)], na.rm = TRUE)) %>%
    dplyr::mutate(type = 0) %>%
    dplyr::mutate(fishery = f,
                  area = 1) %>%
    dplyr::mutate_at(vars(contains("sizebin")), ~./inpN) %>%
    dplyr::select(fishery, area, year, species, type, inpN, everything()) %>%
    dplyr::arrange(fishery, area, species, year)

  allfishlenbin <- bind_rows(allfishlenbin, fishlenbin)
}
write_csv(allfishlenbin, paste0(o.name,"observation_lengths_NOBA_allfisheries.csv"))

@@

Survey and catch datasets in Gavin's suggested format (all surveys together, all fleets together). As above, note that this is just a test. The folder has two different survey and two different fishery configurations; they are not independent. Also, fishery catch is not currently separated into fleets. We wouldn't use all of these in an input file.

@@

#multiple surveys named in list object, use as filename
for(s in names(survObsBiom)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svbio <- survObsBiom[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, year, atoutput) %>%
    dplyr::rename(biomass = atoutput) %>%
    dplyr::mutate(survey = s) %>%
    dplyr::left_join(svcvlook) %>%
    dplyr::select(survey, year, species, everything()) %>%
    dplyr::arrange(survey, species, year)

@@

allcatch <- tibble()

for(f in names(catchbio_ss)){
  catchbio <- catchbio_ss[[f]][[1]] %>%
    dplyr::mutate(year = time/365) %>%
    dplyr::select(species, year, atoutput) %>%
    dplyr::rename(catch = atoutput) %>%
    dplyr::mutate(fishery = f) %>%
    dplyr::mutate(area = 1) %>%
    dplyr::left_join(fcvlook) %>%
    dplyr::select(fishery, area, year, species, everything()) %>%
    dplyr::arrange(fishery, species, year)

  allcatch <- bind_rows(allcatch, catchbio)  
}

write_csv(allcatch, paste0(o.name,"observation_catch_NOBA_allfisheries.csv"))
```
